Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
removing app A

Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then applies the first construction. $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed for the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{On the Relationship to General Obfuscation}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

\paragraph{Open Problems}
Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Alternatively, in case of burst errors~\cite{gilbert1960capacity}, multiple symbols from a small alphabet can be combined into a single symbol from a large alphabet.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.  However, distributions with $\Huse \le 0$ are supported only for large alphabets.  For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.

\lnote{restricting errors instead of entropy is another way to get around impossibility}

\medskip
\lnote{skip if no space}
The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\kappa$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$, then $\Pr[\rep( w', P) = R] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $R$ is pseudorandom conditioned on $P$, that is $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness. In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.

Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.  We follow the second approach.
In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.  To overcome these bounds, we use a computational version of a fuzzy conductor.
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} \lnote{I haven't checked this section below this line}
We now define a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
\begin{itemize}
\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $X\in\{0,1\}^\ell$ and a helper string $SS\in\{0,1\}^*$.
\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $SS\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', SS) = X] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $X$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
\begin{definition}
Let $\chi$ be a finite set.
A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon_{ext}, s_{ext})$-average-case computational extractor} if for all pairs
of random variables $X, Y$ over $\zo^\ell, \chi$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s_{ext}}}((\cext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon_{ext}$.
\end{definition}

@@

\begin{lemma}
\label{lem:cond and cext}
Let $\gen'$, $\rep'$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.  Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.  Define $(\gen, \rep)$ as:
\begin{itemize}
\item $\gen(w; seed):$ run $(x, ss)= \gen'(w)$ and set $r = \cext(x; seed)$, $p = (ss, seed)$.  Output $(r, p)$.
\item $\rep(w, (ss, seed)):$ recover $x = \rec'(w'; p')$ and output $r = \cext(x; seed)$.
\end{itemize}
Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
\end{lemma}

@@

This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers. Goldreich provides an introduction to samplers in~\cite{goldreich1997sample}.

@@

\section{Fuzzy Conductors}
\lnote{I need to check this}
\label{sec:conductors}
Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).  Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.  They suggest these bounds may be avoided by outputting a fresh random variable.  This is known as a fuzzy conductor~\cite{KanukurthiR09}.
\begin{definition}
A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
\begin{enumerate}
\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).  If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.  That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.  This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
\begin{itemize}
\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
\end{itemize}
Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.
\begin{lemma}
The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
\end{lemma}
\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.  Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.  Define $(X,SS) \leftarrow \gen'(W)$.  Then there must exist a distribution $Y$ with $\Hav(Y|SS) \geq \tilde{m}$ such that $\Delta((X,SS), (Y, SS))\leq \epsilon$.  By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.  Now applying Markov's inequality to $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.  Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).  Then $\Delta((X | SS =s^* , s^*), (Y| SS = s^*, s^*))\leq 2\epsilon$ and $\Hoo(Y|SS=s^*)\geq \tilde{m}-1$.  Denote by the set $A'$ the possible values of $X$ when $SS=s^*$.  For the statistical distance property to hold, $|A'| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.  Associate with every $x\in A'$ some $w\in S$ which could have produced $x$ with nonzero probability given $SS=s^*$, and call this map $C$.  $C$ defines an error correcting code with the required parameters.
\end{proof}

@@

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.  In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).

>>>>

Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then applies the first construction. $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed in the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

\paragraph{Open Problems}
Both constructions require a large alphabet $\mathcal{Z}$---one whose size is more than polynomial in the security parameter.\footnote{Codes over large alphabets are often used to correct burst errors~\cite{gilbert1960capacity}.}  It is possible to tweak the sample-then-obfuscate construction for use with a small alphabet.  However, distributions with $\Huse \le 0$ are supported only for large alphabets.  For small alphabets, $\Huse>0$ and there are good information-theoretic constructions known~\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08}.
Constructing a computational fuzzy extractor when $\Huse\le 0$ and a small alphabet is an open problem.

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse\le 0$ is an open problem.

In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key.  A meaningful restriction of correctable errors is an open problem.

\medskip
The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

@@

\begin{definition}~\cite[Definition 2.5]{fuller2013computational}
\label{def:comp fuzzy extractor}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$. A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \kappa, t)$-\emph{computational fuzzy extractor} that is $(\epsilon, s)$-hard with error $\delta$ if \gen and \rep satisfy the following properties:
\begin{itemize}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$, where the probability is over the randomness of $(\gen, \rep)$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $r$ is pseudorandom conditioned on $p$, that is $\delta^{\mathcal{D}_s}((R, P), (U_\kappa, P))\leq \epsilon$.
\end{itemize}
\end{definition}
In the above definition, the errors are chosen before $P$: if the error pattern between $w$ and $w'$ depends on the output of $\gen$, then there is no guarantee about the probability of correctness. In both our constructions it is crucial that $w'$ is chosen independently of the outcome of \gen.

Fuller, Meng, and Reyzin~\cite{fuller2013computational} present two approaches for constructing a computational fuzzy extractor: analyzing the information-reconciliation and privacy amplifications components together or using a fuzzy conductor and a privacy amplification component.  We follow the second approach.
The lower bounds on entropy loss of fuzzy extractors shown by Dodis et al.~\cite[Section C]{DBLP:journals/siamcomp/DodisORS08} extend immediately to fuzzy conductors.  %In \apref{sec:conductors}, we show that information-theoretic fuzzy conductors are subject to the same lower bounds on entropy loss as information-theoretic  fuzzy extractors.  
To overcome these bounds, we use a computational version of a fuzzy conductor.
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

\iffalse
\begin{definition}
\label{def:comp fuzzy cond}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy the following properties (the first two properties are the same as in \defref{def:comp fuzzy extractor}, with $x$ replacing $r$):
\begin{itemize}
\item The generate procedure $\gen$ on input $w\in \mathcal{M}$ outputs a string $x\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure $\rep$ takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(x, p)\leftarrow \gen(w)$, then $\Pr[\rep(w',p) = x] \geq 1-\delta$ where the probability is over the randomness of $(\gen, \rep)$.
If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep$.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $x$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon_{cond}, s_{cond}}(X |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
\fi

A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
\begin{definition}
Let $\chi$ be a finite set.
A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\begin{lemma}
\label{lem:cond and cext}
Let $(\gen'$, $\rep')$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{cond}, s_{cond})$-hard with error $\delta$ and outputs in $\zo^\ell$.  Let $\cext:\zo^\ell\times \zo^d\rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon_{ext}, s_{ext})$-average case computational extractor.  Define $(\gen, \rep)$ as:
\begin{itemize}
\item $\gen(w; seed)$ (where $seed\in \zo^d$): run $(r', p')= \gen'(w)$ and output $r = \cext(r'; seed)$, $p = (p', seed)$. 
\item $\rep(w', (p', seed)):$ run $r' = \rep'(w'; p')$ and output $r = \cext(r'; seed)$.
\end{itemize}
Then $(\gen, \rep)$ is a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon_{cond}+\epsilon_{ext}, s')$-hard with error $\delta$ where $s' = \min\{s_{cond} - |\cext| -d, s_{ext}\}$.
\end{lemma}

@@

This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers. Goldreich provides an introduction to samplers in~\cite{goldreich2011sample}.

@@

%\section{Fuzzy Conductors}
%\lnote{I need to check this}
%\label{sec:conductors}
%Fuzzy extractors  have strong upper bounds on remaining entropy based on the best error correcting codes~(if they provide the same guarantee for all input distributions with the same entropy and error tolerance).  Fuller, Meng, and Reyzin show that computational information-reconciliation techniques are subject to similar bounds~\cite{fuller2013computational}.  They suggest these bounds may be avoided by outputting a fresh random variable.  This is known as a fuzzy conductor~\cite{KanukurthiR09}.
%A $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-\emph{fuzzy conductor} with error $\delta$ is a pair of randomized procedures, ``generate''~(\gen') and ``reproduce''~(\rep'), with the following properties:
%\begin{enumerate}
%\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $x\in\zo^*$ and a helper string $ss\in\zo^*$.
%\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\zo^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w, w')\leq t$, if $X, SS$ were generated by $(X, SS)\leftarrow \gen'(w)$, then $\Pr[\rep(w', SS) = X]\geq 1-\delta$~(over the coins of $\gen', \rep'$).  If $\dis(w, w')>t$, then no guarantee is provided about the output of $\rep'$.
%\item The security property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $X$ is close to a high entropy distribution $Y$.  That is, $\exists Y$ with $\Hav(Y | SS ) \geq \tilde{m}$ such that $\Delta((X, SS), (Y, SS))\leq \epsilon$.
%\end{enumerate}
%\noindent In this section, we show that fuzzy conductors are subject to the same lower bounds as fuzzy extractors.  This motivates our use of a computational fuzzy conductor in \defref{def:comp fuzzy cond}.
%We borrow the following notation from the work of Dodis et al.~\cite{DBLP:journals/siamcomp/DodisORS08}:
%\item A $(\mathcal{M}, K, t)$ code is a subset of $\mathcal{M}$ of size $K$ where a procedure exists that corrects $t$ errors.
%%\item $K(\mathcal{M}, t)$ is the largest $K$ for which there exists an $(\mathcal{M}, K, t)$-code.
%\item $K(\mathcal{M}, t, S)$ is the largest $K$ such that there exists an $(\mathcal{M}, K, t)$ code all of whose $K$ points belong to $S$.
%\item $L(\mathcal{M}, t, m) = \log (\min_{|S| = 2^m} K(\mathcal{M}, t, S))$.  This is the performance of worst error-correcting code for an arbitrary subset of size $2^m$.
%Intuitively, $K(\mathcal{M}, t, S)$ is the size of the best code that covers a given subset and $L(\mathcal{M}, t, m)$ is size of the code that covers the hardest subset in the metric space.
%The existence of a $(\mathcal{M}, m, \tilde{m}, t, \epsilon)$-fuzzy conductor implies that $\tilde{m}\leq L(\mathcal{M}, t, m) +1 -\log (1-2\epsilon)$.
%\begin{proof}  Assume $(\gen', \rep')$ is a fuzzy conductor with the parameters stated.  Let $A$ be a set of size $2^m$ in $\mathcal{M}$ and let $W$ be the uniform distribution over $A$.  Define $(X,SS) \leftarrow \gen'(W)$.  Then there must exist a distribution $Y$ with $\Hav(Y|SS) \geq \tilde{m}$ such that $\Delta((X,SS), (Y, SS))\leq \epsilon$.  By Markov's inequality, there exists some set $B_{SS}$ such that $\Pr[ss\in B_{SS}] \geq 1/2$ and $\forall s\in B_{SS}$ one has $\Delta(X | SS = s, s ), (Y | SS = s, s)<2\epsilon$.  Now applying Markov's inequality to $\max_{Y} \Pr[Y=y | SS=s]$, there exists a set $B_{SS'}$ such that $\Pr[SS\in B_{SS'}]>1/2$, and for all $s\in B_{SS'}$, $\Hoo(Y| SS =s ) \geq \tilde{m}-1$.  Denote by $s^*$ a value in $B_{SS}\cap B_{SS'}$~(one value must exist).  Then $\Delta((X | SS =s^* , s^*), (Y| SS = s^*, s^*))\leq 2\epsilon$ and $\Hoo(Y|SS=s^*)\geq \tilde{m}-1$.  Denote by the set $A'$ the possible values of $X$ when $SS=s^*$.  For the statistical distance property to hold, $|A'| \geq  (1-2\epsilon)2^{\tilde{m}-1}$.  Associate with every $x\in A'$ some $w\in S$ which could have produced $x$ with nonzero probability given $SS=s^*$, and call this map $C$.  $C$ defines an error correcting code with the required parameters.

@@

\defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.  In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).  We first show some sources that are unguessable block distributions~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block distributions~(\secref{sec:negative ex}).

\subsection{Positive Examples}
\label{sec:positive ex}
We begin with the case of independent blocks.
